From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Reworked Section 5.1 and 5.2.

In order to get an idea of the coverage of the two knowledge bases,
we have further created a~spatio-temporal visualization of Freebase and Wikidata
that is shown in \autoref{fig:time-space}.

We extracted the earliest date and the longitude
linked to each of the entities of the two knowledge bases.
We then propagated them to the connected entities that do not have such data.
To implement this propagation, we set as value (date or longitude)
the average of the values of the entities whose distance is $<10$
with a~weight of $2^{-d}$ (with $d$~being the distance between the two entities).

We see that the two knowledge bases display the same basic patterns,
with their coverage mostly concentrated on the longitudes of Europe and North America.
There are no strong differences between them,
yet coverage of \mbox{\emph{post}-year-2000} entities seems stronger in Freebase.

@@

One possible conclusion from this visualization could be that Wikidata,
despite its smaller absolute size, appears to have
a~nearly as complete coverage of the world as Freebase.
Nonetheless, it is very challenging to find objective ways to compare the two databases
and good metrics of success for the migration.
We certainly can note that for data sets to be added to a~knowledge bases,
the raw number of triples is not an adequate measure of quality.

>>>>

In order to get an idea of the coverage of the two knowledge bases,
we have further created a~spatio-temporal visualization of Freebase and Wikidata
that is shown in \autoref{fig:time-space}.
We extracted the earliest date and the longitude
linked to each of the entities of the two knowledge bases.
We then propagated them to the connected entities that do not have such data.
To implement this propagation, we set as value (date or longitude)
the average of the values of the entities whose distance is $<10$
with a~weight of $2^{-d}$ (with $d$~being the distance between the two entities).

We see that the two knowledge bases display the same basic patterns,
with their coverage mostly concentrated on the longitudes of Europe and North America.
There are no strong differences between them,
yet coverage of \emph{post}-year-2000 entities seems stronger in Freebase.

@@

One possible conclusion from this visualization could be that Wikidata,
despite its smaller absolute size, appears to have
a~nearly as complete coverage of the world as Freebase.
Nonetheless, it is very challenging to find objective ways to compare the two databases
and good metrics of success for the migration.
We certainly can note that for data sets to be added to a~knowledge bases,
the raw number of triples is \emph{not} an adequate measure of quality.
